Learning action models with minimal observability

### 2018-07-31 doc/aij18/experiments.tex
updated section 6 AIJ18 paper

\item {\bf Planner}. The classical planner we use to solve the $P_\Lambda$ instances that result from our compilations is {\sc Madagascar}~\cite{rintanen2014madagascar}. We use {\sc Madagascar} for two reasons:
  \begin{enumerate}
  \item  Its ability to deal with planning instances populated with dead-ends.
  \item  It can levarage the horizon of the solution plan, when it is known. Recall that, when the length of the plan traces is known (\FO action sequences or \FO state trajectories) the horizon of the solution plan is also known. SAT-based planners can apply the actions for programming preconditions in parallel during a single planning step (and the same for actions programming effects) because these actions do not interact. Hence, we know that the programming prefix of a solution plan can be solved in two steps, independently of the number of programming actions applied.
  \end{enumerate}

@@

\begin{figure}[hbt!]
	\centering
	\includegraphics[width=0.8\linewidth]{figures/input_size_100_10_precision.eps}
	\caption{Evaluation of the impact of the input size on the quality of the learned models when learning from plan traces with \FO action sequences and \PO state trajectories with 10\% observability}
	\label{fig:np_quality}
\end{figure}

\begin{figure}[hbt!]
	\centering
	\includegraphics[width=0.8\linewidth]{figures/input_size_100_10_time.eps}
	\caption{Evaluation of the impact of the input size on the computation time when learning from plan traces with \FO action sequences and \PO state trajectories with 10\% observability}
	\label{fig:np_time}
\end{figure}

\newpage
Figure~\ref{fig:pspace_quality} reports the {\em precision} and {\em recall} of the models learned by our approach in the PSPACE-complete scenario (NO action sequence and NO state trajectory). The quality of the learned models is now lower than in the previous case (the NP-complete scenario) and a quality drop appears as the amount of input knowledge increases. This is caused by an increasing number of timeouts in the experiments, meaning that no solution is found. The computation time in this scenario (figure \ref{fig:pspace_time}) is also considerably higher given the complexity of the task, which is reflected on the amount of timeouts.

\begin{figure}[hbt!]
	\centering
	\includegraphics[width=0.65\linewidth]{figures/input_size_0_0_precision.eps}
	\caption{Evaluation of the impact of the input size on the quality of the learned models when learning from plan traces with \NO action sequences and \NO state trajectories}
	\label{fig:pspace_quality}
\end{figure}
\begin{figure}[hbt!]
	\centering
	\includegraphics[width=0.65\linewidth]{figures/input_size_0_0_time.eps}
	\caption{Evaluation of the impact of the input size on the computation time when learning from plan traces with \NO action sequences and \NO state trajectories}
	\label{fig:pspace_time}
\end{figure}

The conclusion we can draw is that learning from few input samples is both our strong point and our limitation. Results on the NP-complete scenario show that the learned models are considerably sound and complete (to put these results into a richer perspective we will also compare ourselves with another approach in the following section). The PSPACE-complete scenario, on the other hand, shows that the learned models have less quality. Nevertheless, we argue that syntax-based metrics are not appropriate for the PSPACE-complete scenario due to the vast amount of reformulations that can appear in such under-constrained learning task and we will show proof of this in section \ref{minimal}.

\subsection{Comparison with \ARMS}
Here we compare the performance of \FAMA to that of \ARMS, one of the most well-known approaches learning planning models. \ARMS works under the assumption of plan traces with \FO action sequences and \NO state trajectories, so we will also adopt this assumption (\ARMS, as any other previous approaches for learning planning models cannot handle the PSPACE-complete scenarios).

We define a \emph{degree of observability} $\sigma$ for the state trajectory, ranging from 0\% to 100\%, that measures the probability of observing a literal, and evaluate both approaches as $\sigma$ increases using 5 plan traces as input. Note that when $\sigma = 0$ we have a \NO state trajectory, when $\sigma=100$ we have a \FO state trajectory and all cases in-between correspond to the \PO scenario. Figures \ref{fig:comparison_precision} and \ref{fig:comparison_recall} compare \FAMA and \ARMS in terms of precision and recall. The horizontal axis represents the degree of observability, while the vertical axis show the average precision (figure \ref{fig:comparison_precision}) or recall (figure \ref{fig:comparison_recall}) computed over the fourteen tested domains. Remarkably, figure \ref{fig:comparison_precision} shows that \FAMA dominates in terms of precision in all cases save for \FO state trajectories. Furthermore, in average, the models learned by our approach are 15\% to 24\% more precise than those learned by \ARMS. A similar conclusion can be drawn for recall (figure \ref{fig:comparison_recall}), where the difference is even larger, meaning that our models are more complete.

\begin{figure}[hbt!]
	\centering
	\includegraphics[width=.8\linewidth]{figures/comparison_precision.eps}
	\caption{Precision comparison between \FAMA and \ARMS}
	\label{fig:comparison_precision}
\end{figure}

\begin{figure}[hbt!]
	\centering
	\includegraphics[width=.8\linewidth]{figures/comparison_recall.eps}
	\caption{Recall comparison between \FAMA and \ARMS}
	\label{fig:comparison_recall}
\end{figure}

@@

\FAMA outperforms \ARMS in this particular experiment, which is one with very limited input. By no means do these results imply that our approach is overall better for the NP-complete scenarios, just that it is able to learn better models when few plan traces are available. We are not reporting experiments where far more input traces are available, since \FAMA cannot handle so much input.

\subsection{Experiments with minimal input knowledge}
\label{minimal}
%In the previous experiments we have given a general view of the performance of \FAMA under different conditions.
So far, experiments have shown that \FAMA is able to learn with very small amounts of input knowledge, be it due to low observability or few training samples. In this section we want to take a closer look at the action models learned from minimal input knowledge. To that end, we will limit the input to only 2 plan traces and analyze the results under different levels of observability.

In this experiment we evaluate three case studies, the first one being an NP-complete scenario and the other two being PSPACE-complete:
\begin{itemize}
	\item \textbf{\FO action sequence and \PO state trajectory}: We are, once again, assuming a degree of observability of 10\% for the state trajectory. The results of this case study are detailed in table \ref{tab:results_minimum_100_10}
	\item  \textbf{\PO action sequence and \PO state trajectory}: In this case study we are assuming a degree of observability of 30\% for both the action sequence and state trajectory. The results of this case study are detailed in table \ref{tab:results_minimum_30_30}
	\item  \textbf{\NO action sequence and \NO state trajectory}: Both the action sequence and state trajectory are completely empty and only initial and final states are observed, i.e., $\tau = \tup{s_0, s_m}, \forall \tau \in \mathcal{T}$. The results of this case study are detailed in table \ref{tab:results_minimum_0_0}
\end{itemize}

All tables in this section (tables \ref{tab:results_minimum_100_10}, \ref{tab:results_minimum_0_0}, \ref{tab:results_minimum_30_30}) follow the same structure. In these tables precision ({\bf P}) and recall ({\bf R}) are computed separately for the preconditions ({\bf Pre}), positive effects ({\bf Add}) and negative Effects ({\bf Del}), and also globally ({\bf Global}). The last column reports the computation time in seconds needed to obtain the learned models. Missing values in the tables correspond to domains where no solution was found given a timeout of 1800 s.

\begin{table}[hbt!]
		\begin{center}

			\begin{tabular}{l|l|l|l|l|l|l||l|l|l|}
				& \multicolumn{2}{|c|}{\bf Pre} & \multicolumn{2}{|c|}{\bf Add} & \multicolumn{2}{|c||}{\bf Del} & \multicolumn{2}{|c|}{\bf Global} & \\ \cline{2-9}			
				& \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c||}{\bf R} &  \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & {\bf Time} \\
				\hline
				blocks & 0.86 & 0.67 & 0.86 & 0.67 & 0.8 & 0.44 & 0.84 & 0.59& 0.21 \\ % [(u'pick-up', u'pick-up', 1), (u'put-down', u'put-down', 1), (u'stack', u'stack', 1, 2), (u'unstack', u'unstack', 1, 2)]
				driverlog & 0.68 & 0.93 & 0.5 & 0.57 & 0.83 & 0.71 & 0.67 & 0.79& 0.27 \\ % [(u'load-truck', u'load-truck', 1, 2, 3), (u'unload-truck', u'unload-truck', 1, 2, 3), (u'board-truck', u'board-truck', 1, 2, 3), (u'disembark-truck', u'disembark-truck', 1, 2, 3), (u'walk', u'walk', 1, 2, 3), (u'drive-truck', u'drive-truck', 1, 2, 3, 4)]
				ferry & 0.78 & 1.0 & 0.5 & 1.0 & 1.0 & 1.0 & 0.71 & 1.0& 0.4 \\ % [(u'sail', u'sail', 1, 2), (u'board', u'board', 1, 2), (u'debark', u'debark', 1, 2)]
				floor-tile & 0.69 & 1.0 & 0.45 & 0.91 & 1.0 & 0.82 & 0.65 & 0.93& 1.42 \\ % [(u'change-color', u'change-color', 1, 2, 3), (u'up', u'up', 1, 2, 3), (u'down', u'down', 1, 2, 3), (u'right', u'right', 1, 2, 3), (u'left', u'left', 1, 2, 3), (u'paint-up', u'paint-up', 1, 2, 3, 4), (u'paint-down', u'paint-down', 1, 2, 3, 4)]
				grid & 0.76 & 0.94 & 0.55 & 0.86 & 1.0 & 1.0 & 0.74 & 0.94& 0.7 \\ % [(u'move', u'move', 1, 2), (u'pickup', u'pickup', 1, 2), (u'putdown', u'putdown', 1, 2), (u'pickup-and-loose', u'pickup-and-loose', 1, 2, 3), (u'unlock', u'unlock', 1, 2, 3, 4)]
				gripper-strips & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0& 0.16 \\ % [(u'move', u'move', 1, 2), (u'pick', u'pick', 1, 2, 3), (u'drop', u'drop', 1, 2, 3)]
				hanoi & 0.67 & 1.0 & 0.67 & 1.0 & 1.0 & 1.0 & 0.73 & 1.0& 0.31 \\ % [(u'move', u'move', 1, 2, 3)]
				miconic & 1.0 & 1.0 & 0.5 & 1.0 & 1.0 & 1.0 & 0.8 & 1.0& 0.29 \\ % [(u'board', u'board', 1, 2), (u'depart', u'depart', 1, 2), (u'up', u'up', 1, 2), (u'down', u'down', 1, 2)]
				n-puzzle & 0.75 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.88 & 1.0& 0.28 \\ % [(u'move', u'move', 1, 2, 3)]
				parking & 0.73 & 0.79 & 0.7 & 0.78 & 1.0 & 0.78 & 0.78 & 0.78& 0.65 \\ % [(u'move-curb-to-curb', u'move-curb-to-curb', 1, 2, 3), (u'move-curb-to-car', u'move-curb-to-car', 1, 2, 3), (u'move-car-to-curb', u'move-car-to-curb', 1, 2, 3), (u'move-car-to-car', u'move-car-to-car', 1, 2, 3)]
				satellite & 0.93 & 1.0 & 0.63 & 1.0 & 1.0 & 0.75 & 0.85 & 0.96& 0.36 \\ % [(u'switch-on', u'switch-on', 1, 2), (u'switch-off', u'switch-off', 1, 2), (u'turn-to', u'turn-to', 1, 2, 3), (u'calibrate', u'calibrate', 1, 2, 3), (u'take-image', u'take-image', 1, 2, 3, 4)]
				transport & 1.0 & 1.0 & 0.71 & 1.0 & 1.0 & 0.6 & 0.9 & 0.9& 0.22 \\ % [(u'drive', u'drive', 1, 2, 3), (u'pick-up', u'pick-up', 1, 2, 3, 4, 5), (u'drop', u'drop', 1, 2, 3, 4, 5)]
				grid-visit-all & 0.67 & 1.0 & 0.5 & 1.0 & 1.0 & 1.0 & 0.63 & 1.0& 0.87 \\ % [(u'move', u'move', 1, 2)]
				zeno-travel & 0.92 & 0.79 & 0.6 & 0.86 & 0.8 & 0.57 & 0.78 & 0.75& 0.26 \\ % [(u'board', u'board', 1, 2, 3), (u'debark', u'debark', 1, 2, 3), (u'refuel', u'refuel', 1, 2, 3, 4), (u'fly', u'fly', 1, 2, 3, 4, 5), (u'zoom', u'zoom', 1, 2, 3, 4, 5, 6)]
				\hline
				\bf & 0.82 & 0.94 & 0.66 & 0.90 & 0.96 & 0.83 & 0.78 & 0.90 & 0.46 \\
			\end{tabular}

		\end{center}
	\caption{\small {\em Precision} and {\em recall} scores for learning tasks with \FO action sequences and \PO state trajectories with 10\% observability}
	\label{tab:results_minimum_100_10}
\end{table}

Table \ref{tab:results_minimum_100_10} shows the results of the first case study. As was expected from the previous experiments, the recall scores are generally higher than the precision ones, and, in fact, the models learned for 6 of the tested domains were perfectly complete. Although precision is overall lower, it is interesting to notice that the soundness of most learned sets of positive effects is flawless. With regards to the computation time, we find times below the second in all cases except for one, "floor-tile", the most complex among the tested domains.

\begin{table}[hbt!]
	\begin{center}

>>>>

\item {\bf Planner}. The classical planner we use to solve the $P_\Lambda$ instances that result from our compilations is {\sc Madagascar}~\cite{rintanen2014madagascar}. We use {\sc Madagascar} for two reasons:
  \begin{enumerate}
  \item  Its ability to deal with planning instances populated with dead-ends.
  \item  It can leverage the horizon of the solution plan, when it is known. Recall that, when the length of the plan traces is known (\FO action sequences or \FO state trajectories) the horizon of the solution plan is also known. SAT-based planners can apply the actions for programming preconditions in parallel during a single planning step (and the same for actions programming effects) because these actions do not interact. Hence, we know that the programming prefix of a solution plan can be solved in two steps, independently of the number of programming actions applied.
  \end{enumerate}

@@

\begin{figure}[hbt!]
	\centering
	\includegraphics[width=0.7\linewidth]{figures/input_size_100_10_precision.eps}
	\caption{{\em Precision} and {\em recall} when learning from [1-10] plan traces with \FO action sequences and \PO state trajectories with 10\% observability.}
	\label{fig:np_quality}
\end{figure}

\begin{figure}[hbt!]
	\centering
	\includegraphics[width=0.7\linewidth]{figures/input_size_100_10_time.eps}
	\caption{Computation time when learning from [1-10] plan traces with \FO action sequences and \PO state trajectories with 10\% observability.}
	\label{fig:np_time}
\end{figure}

\newpage
Figure~\ref{fig:pspace_quality} reports {\em precision} and {\em recall} for the models learned by our approach in the PSPACE-complete scenario (NO action sequence and NO state trajectory). The {\em precision} and {\em recall} values are now lower and they drop as the amount of input knowledge increases. For the PSPACE-complete scenario, {\em precision} and {\em recall} scores have to be taken with a grain of salt because {\bf pure syntax-based metrics are not informative when reformulations appear}. This is the case of such an under-constrained learning task and we provide experimental evidence of this in Section \ref{minimal}. Further, the score drop reflects an increasing number of timeouts meaning that, no solution is found for several domains within the given time-bound. Computation time (Figure \ref{fig:pspace_time}) is also higher explained again by this larger number of timeouts produced in a scenario with larger worst case complexity.

\begin{figure}[hbt!]
	\centering
	\includegraphics[width=0.7\linewidth]{figures/input_size_0_0_precision.eps}
	\caption{{\em Precision} and {\em recall} when learning from [1-10] plan traces with \NO action sequences and \NO state trajectories.}
	\label{fig:pspace_quality}
\end{figure}
\begin{figure}[hbt!]
	\centering
	\includegraphics[width=0.7\linewidth]{figures/input_size_0_0_time.eps}
	\caption{Computation time when learning from [1-10] plan traces with \NO action sequences and \NO state trajectories.}
	\label{fig:pspace_time}
\end{figure}

%The conclusion we can draw is that learning from few input samples is both our strong point and our limitation. Results on the NP-complete scenario show that the learned models are considerably sound and complete (to put these results into a richer perspective we will also compare ourselves with another approach in the following section). The PSPACE-complete scenario, on the other hand, shows that the learned models have less quality. Nevertheless, we argue that syntax-based metrics are not appropriate for the PSPACE-complete scenario due to the vast amount of reformulations that can appear in such under-constrained learning task and we will show proof of this in section \ref{minimal}.

\subsection{Comparison with \ARMS}
Now we compare the performance of \FAMA to that of \ARMS. \ARMS assumes input plan traces with \FO action sequences and \NO state trajectories so here, we will also adopt this assumption (\ARMS, as any other previous approaches for learning planning models cannot handle the PSPACE-complete scenario).

We define a \emph{degree of observability} $\sigma$ for the state trajectory, ranging from 0\% to 100\%, that measures the probability of observing a literal, and evaluate both approaches as $\sigma$ increases using 5 plan traces as input. When $\sigma = 0$ we have a \NO state trajectory, when $\sigma=100$ we have a \FO state trajectory and all cases in-between correspond to the \PO scenario. Figures \ref{fig:comparison_precision} and \ref{fig:comparison_recall} compare \FAMA and \ARMS in terms of {\em precision} and {\em recall}. Horizontal axes represents the degree of observability, while vertical axes show the average {\em precision} (Figure \ref{fig:comparison_precision}) or {\em recall} (Figure \ref{fig:comparison_recall}). \FAMA dominates in terms of {\em precision} in all cases (the models learned by our approach are 15\% to 24\% more precise than those learned by \ARMS) except for \FO state trajectories. A similar trend is drawn for {\em recall} (Figure \ref{fig:comparison_recall}), where the difference is even larger, meaning that our learned models are more complete. These results evidence the \FAMA capacity to learn better models when few plan traces are available but do not imply that our approach is overall better for NP-complete scenarios (Figure~\ref{fig:np_time} showed that \FAMA cannot handle so much input as \ARMS).

\begin{figure}[hbt!]
	\centering
	\includegraphics[width=.65\linewidth]{figures/comparison_precision.eps}
	\caption{{\em Precision} comparison between \FAMA and \ARMS for different \emph{degrees of observability}.}
	\label{fig:comparison_precision}
\end{figure}

\begin{figure}[hbt!]
	\centering
	\includegraphics[width=.65\linewidth]{figures/comparison_recall.eps}
	\caption{{\em Recall} comparison between \FAMA and \ARMS for different \emph{degrees of observability}.}
	\label{fig:comparison_recall}
\end{figure}

@@

\subsection{Learning with minimal input knowledge}
\label{minimal}
%In the previous experiments we have given a general view of the performance of \FAMA under different conditions. So far, experiments have shown that \FAMA is able to learn with very small amounts of input knowledge, be it due to low observability or few training samples.
Let us take a closer look at the action models learned from minimal input knowledge. To that end, we will limit the input to only 2 plan traces and analyze the results under different levels of observability. In this experiment we evaluate three cases of study, the first one being an NP-complete scenario and the other two being PSPACE-complete:
\begin{itemize}
	\item \textbf{\FO action sequence and \PO state trajectory}: We are, once again, assuming a degree of observability of 10\% for the state trajectory. The results of this case study are detailed in Table \ref{tab:results_minimum_100_10}.
	\item  \textbf{\PO action sequence and \PO state trajectory}: In this case study we are assuming a degree of observability of 30\% for both the action sequence and state trajectory. The results of this case study are detailed in Table \ref{tab:results_minimum_30_30}.
	\item  \textbf{\NO action sequence and \NO state trajectory}: Both the action sequence and state trajectory are completely empty so only the initial and final states are observed, i.e., $\tau = \tup{s_0, s_m}, \forall \tau \in \mathcal{T}$. The results of this case study are detailed in Table \ref{tab:results_minimum_0_0}.
\end{itemize}

All tables in this section (Tables \ref{tab:results_minimum_100_10}, \ref{tab:results_minimum_30_30} and \ref{tab:results_minimum_0_0}) follow the same structure. {\em Precision} ({\bf P}) and {\em Recall} ({\bf R}) scores are computed separately for the preconditions ({\bf Pre}), positive effects ({\bf Add}) and negative Effects ({\bf Del}), and also globally ({\bf Global}). The last column reports the computation time (in seconds) needed to obtain the learned models. Missing values in the tables (-) correspond to domains where no solution was found given a timeout of 1800 s.

Table \ref{tab:results_minimum_100_10} shows the results of the first case study. Recall scores are generally higher than the precision ones, and, in fact, the models learned for six out of the fourteen domains were perfectly complete. Although precision is overall lower, it is interesting to notice that the soundness of most learned sets of positive effects is flawless. With regards to the computation time, we find times below the second in all cases except for the {\em floor-tile} domain.

\begin{table}[hbt!]
		\begin{center}
                  \begin{footnotesize}			
			\begin{tabular}{l|l|l|l|l|l|l||l|l||l|}
				& \multicolumn{2}{|c|}{\bf Pre} & \multicolumn{2}{|c|}{\bf Add} & \multicolumn{2}{|c||}{\bf Del} & \multicolumn{2}{|c|}{\bf Global} & \\ \cline{2-9}			
				& \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c||}{\bf R} &  \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & {\bf Time} \\
				\hline
				blocks & 0.86 & 0.67 & 0.86 & 0.67 & 0.8 & 0.44 & 0.84 & 0.59& 0.21 \\ % [(u'pick-up', u'pick-up', 1), (u'put-down', u'put-down', 1), (u'stack', u'stack', 1, 2), (u'unstack', u'unstack', 1, 2)]
				driverlog & 0.68 & 0.93 & 0.5 & 0.57 & 0.83 & 0.71 & 0.67 & 0.79& 0.27 \\ % [(u'load-truck', u'load-truck', 1, 2, 3), (u'unload-truck', u'unload-truck', 1, 2, 3), (u'board-truck', u'board-truck', 1, 2, 3), (u'disembark-truck', u'disembark-truck', 1, 2, 3), (u'walk', u'walk', 1, 2, 3), (u'drive-truck', u'drive-truck', 1, 2, 3, 4)]
				ferry & 0.78 & 1.0 & 0.5 & 1.0 & 1.0 & 1.0 & 0.71 & 1.0& 0.4 \\ % [(u'sail', u'sail', 1, 2), (u'board', u'board', 1, 2), (u'debark', u'debark', 1, 2)]
				floor-tile & 0.69 & 1.0 & 0.45 & 0.91 & 1.0 & 0.82 & 0.65 & 0.93& 1.42 \\ % [(u'change-color', u'change-color', 1, 2, 3), (u'up', u'up', 1, 2, 3), (u'down', u'down', 1, 2, 3), (u'right', u'right', 1, 2, 3), (u'left', u'left', 1, 2, 3), (u'paint-up', u'paint-up', 1, 2, 3, 4), (u'paint-down', u'paint-down', 1, 2, 3, 4)]
				grid & 0.76 & 0.94 & 0.55 & 0.86 & 1.0 & 1.0 & 0.74 & 0.94& 0.7 \\ % [(u'move', u'move', 1, 2), (u'pickup', u'pickup', 1, 2), (u'putdown', u'putdown', 1, 2), (u'pickup-and-loose', u'pickup-and-loose', 1, 2, 3), (u'unlock', u'unlock', 1, 2, 3, 4)]
				gripper-strips & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0& 0.16 \\ % [(u'move', u'move', 1, 2), (u'pick', u'pick', 1, 2, 3), (u'drop', u'drop', 1, 2, 3)]
				hanoi & 0.67 & 1.0 & 0.67 & 1.0 & 1.0 & 1.0 & 0.73 & 1.0& 0.31 \\ % [(u'move', u'move', 1, 2, 3)]
				miconic & 1.0 & 1.0 & 0.5 & 1.0 & 1.0 & 1.0 & 0.8 & 1.0& 0.29 \\ % [(u'board', u'board', 1, 2), (u'depart', u'depart', 1, 2), (u'up', u'up', 1, 2), (u'down', u'down', 1, 2)]
				n-puzzle & 0.75 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.88 & 1.0& 0.28 \\ % [(u'move', u'move', 1, 2, 3)]
				parking & 0.73 & 0.79 & 0.7 & 0.78 & 1.0 & 0.78 & 0.78 & 0.78& 0.65 \\ % [(u'move-curb-to-curb', u'move-curb-to-curb', 1, 2, 3), (u'move-curb-to-car', u'move-curb-to-car', 1, 2, 3), (u'move-car-to-curb', u'move-car-to-curb', 1, 2, 3), (u'move-car-to-car', u'move-car-to-car', 1, 2, 3)]
				satellite & 0.93 & 1.0 & 0.63 & 1.0 & 1.0 & 0.75 & 0.85 & 0.96& 0.36 \\ % [(u'switch-on', u'switch-on', 1, 2), (u'switch-off', u'switch-off', 1, 2), (u'turn-to', u'turn-to', 1, 2, 3), (u'calibrate', u'calibrate', 1, 2, 3), (u'take-image', u'take-image', 1, 2, 3, 4)]
				transport & 1.0 & 1.0 & 0.71 & 1.0 & 1.0 & 0.6 & 0.9 & 0.9& 0.22 \\ % [(u'drive', u'drive', 1, 2, 3), (u'pick-up', u'pick-up', 1, 2, 3, 4, 5), (u'drop', u'drop', 1, 2, 3, 4, 5)]
				grid-visit-all & 0.67 & 1.0 & 0.5 & 1.0 & 1.0 & 1.0 & 0.63 & 1.0& 0.87 \\ % [(u'move', u'move', 1, 2)]
				zeno-travel & 0.92 & 0.79 & 0.6 & 0.86 & 0.8 & 0.57 & 0.78 & 0.75& 0.26 \\ % [(u'board', u'board', 1, 2, 3), (u'debark', u'debark', 1, 2, 3), (u'refuel', u'refuel', 1, 2, 3, 4), (u'fly', u'fly', 1, 2, 3, 4, 5), (u'zoom', u'zoom', 1, 2, 3, 4, 5, 6)]
				\hline
				\bf & 0.82 & 0.94 & 0.66 & 0.90 & 0.96 & 0.83 & 0.78 & 0.90 & 0.46 \\
			\end{tabular}
                  \end{footnotesize}			
		\end{center}
	\caption{\small {\em Precision} and {\em recall} scores for learning tasks with \FO action sequences and \PO state trajectories with 10\% observability.}
	\label{tab:results_minimum_100_10}
\end{table}

In Table \ref{tab:results_minimum_30_30}, which collects the result of the PSPACE case study with 30\% observability, the scores for some domains are missing. This is the case for {\em floor-tile}, and {\em parking} both considered \emph{puzzle-like} domains and that put a strain on the planners. Interestingly enough, {\em hanoi} also qualifies as a \emph{puzzle-like} domain, and we can see how this is reflected on the computation time. With regards to the learned models, we find that they retain similar level of soundness, while their completeness is lower than in the previous case study. This is specially the case for the preconditions, which have gone from 0.94 recall to 0.54. %This results are difficult to explain, given that in this case study the intermediate states contain more information, but
The explanation for these scores is that input actions are strong constraints that play a key role on how close the learned model are with respect to the GTM. The more these actions are missing the more present is reformulation and pure syntax-based metrics become less relevant.

\begin{table}[hbt!]
	\begin{center}
		\begin{footnotesize}
		\begin{tabular}{l|l|l|l|l|l|l||l|l||l|}
			& \multicolumn{2}{|c|}{\bf Pre} & \multicolumn{2}{|c|}{\bf Add} & \multicolumn{2}{|c||}{\bf Del} & \multicolumn{2}{|c|}{\bf Global} & \\ \cline{2-9}			
			& \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c||}{\bf R} &  \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & {\bf Time} \\
			\hline
			blocks & 1.0 & 0.89 & 0.9 & 1.0 & 1.0 & 0.89 & 0.96 & 0.93& 3.51 \\ % [(u'pick-up', u'put-down', 1), (u'put-down', u'pick-up', 1), (u'stack', u'stack', 1, 2), (u'unstack', u'unstack', 1, 2)]
			driverlog & 0.3 & 0.21 & 0.31 & 0.57 & 0.29 & 0.29 & 0.3 & 0.32& 24.41 \\ % [(u'load-truck', u'unload-truck', 1, 2, 3), (u'unload-truck', u'load-truck', 1, 2, 3), (u'board-truck', u'board-truck', 1, 2, 3), (u'disembark-truck', u'disembark-truck', 1, 2, 3), (u'walk', u'walk', 2, 1, 3), (u'drive-truck', u'drive-truck', 1, 2, 3, 4)]
			ferry & 0.83 & 0.71 & 0.8 & 1.0 & 1.0 & 1.0 & 0.87 & 0.87& 4.39 \\ % [(u'sail', u'sail', 1, 2), (u'board', u'board', 1, 2), (u'debark', u'debark', 1, 2)]
			floor-tile & - & - & - & - & - & - & - & - & - \\ % [(u'change-color', u'change-color', 1, 2, 3), (u'up', u'change-color', 1, 3, 2), (u'down', u'up', 1, 2, 3), (u'right', u'up', 1, 3, 2), (u'left', u'down', 1, 3, 2), (u'paint-up', u'paint-up', 1, 2, 3, 4), (u'paint-down', u'paint-down', 1, 2, 3, 4)]
			grid & - & - & - & - & - & - & - & - & - \\ % [(u'move', u'move', 1, 2), (u'pickup', u'move', 2, 1), (u'putdown', u'putdown', 1, 2), (u'pickup-and-loose', u'pickup-and-loose', 1, 2, 3), (u'unlock', u'unlock', 1, 2, 3, 4)]
			gripper-strips & 1.0 & 0.67 & 0.8 & 1.0 & 1.0 & 1.0 & 0.92 & 0.86& 1.31 \\ % [(u'move', u'move', 1, 2), (u'pick', u'pick', 1, 2, 3), (u'drop', u'drop', 1, 2, 3)]
			hanoi & 1.0 & 0.5 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.75& 1566.44 \\ % [(u'move', u'move', 1, 2, 3)]
			miconic & 0.75 & 0.33 & 0.5 & 0.75 & 0.5 & 0.67 & 0.57 & 0.5& 0.86 \\ % [(u'board', u'board', 1, 2), (u'depart', u'depart', 1, 2), (u'up', u'up', 2, 1), (u'down', u'down', 1, 2)]
			n-puzzle & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0& 62.82 \\ % [(u'move', u'move', 1, 2, 3)]
			parking & - & - & - & - & - & - & - & - & - \\ % [(u'move-curb-to-curb', u'move-curb-to-curb', 1, 2, 3), (u'move-curb-to-car', u'move-curb-to-curb', 1, 3, 2), (u'move-car-to-curb', u'move-curb-to-car', 1, 2, 3), (u'move-car-to-car', u'move-car-to-curb', 1, 2, 3)]
			satellite & 0.78 & 0.5 & 0.57 & 0.8 & 0.33 & 0.25 & 0.63 & 0.52& 22.76 \\ % [(u'switch-on', u'switch-on', 1, 2), (u'switch-off', u'switch-off', 1, 2), (u'turn-to', u'turn-to', 1, 2, 3), (u'calibrate', u'calibrate', 1, 2, 3), (u'take-image', u'take-image', 1, 2, 3, 4)]
			transport & 0.5 & 0.3 & 0.43 & 0.6 & 0.5 & 0.4 & 0.47 & 0.4& 31.07 \\ % [(u'drive', u'drive', 1, 2, 3), (u'pick-up', u'pick-up', 1, 2, 3, 5, 4), (u'drop', u'drop', 1, 2, 3, 5, 4)]
			grid-visit-all & 1.0 & 0.5 & 0.5 & 0.5 & 1.0 & 1.0 & 0.75 & 0.6& 3.11 \\ % [(u'move', u'move', 1, 2)]
			zeno-travel & 0.67 & 0.29 & 0.75 & 0.43 & 0.75 & 0.43 & 0.71 & 0.36& 494.2 \\ % [(u'board', u'board', 1, 2, 3), (u'debark', u'debark', 1, 2, 3), (u'refuel', u'refuel', 1, 2, 3, 4), (u'fly', u'fly', 1, 3, 2, 5, 4), (u'zoom', u'zoom', 1, 2, 3, 4, 5, 6)]
			\hline
			\bf & 0.80 & 0.54 & 0.69 & 0.79 & 0.76 & 0.72 & 0.74 & 0.65 & 201.35

		\end{tabular}
		\end{footnotesize}
	\end{center}
	\caption{\small {\em Precision} and {\em recall} scores for learning tasks with \PO action sequences and \PO state trajectories with 30\% observability in both cases.}
	\label{tab:results_minimum_30_30}
\end{table}

The effect of missing input actions is more evident in our last case study with \NO action sequences and state trajectories (Table \ref{tab:results_minimum_0_0}). In this case we are able to find solutions for all domains. Search is even less constrained so there are far more possible solutions for this learning task. This wider range of solutions is also evidenced by the kind of the learned models, which in spite of being compliant with the input data, are further from the original GTM. In the table we find that both precision and recall have seen their scores decreased to 0.6 and 0.5, respectively. Syntax-based metrics are not appropriate for scenarios with minimal observability as they cannot cope with the \emph{reformulations} that frequently occur in these circumstances.

To illustrate this, Figure \ref{fig:macroaction} shows the PDDL encoding of the action model of the {\tt stack} operator learned from plan traces with \NO action sequences and state trajectories. This action model removes a block from on top of another block and puts it down on the table, all done in a single step. There are two main differences from the GTM for {\tt stack}: 1) the learned action is unstacking a block instead of stacking it, and 2) the block ends on the table after the action is applied, working as an {\tt unstack + put-down} \emph{macro-action}. We refer to the first difference as \emph{role swapping} and it happens when actions are removed from the trace. If no actions are present in the input traces, the name of actions becomes meanless (actions are effectively anonymous), meaning that they can interchange their behavior with any comparable action model. The second issue can happen if there are missing states in the input traces.
